\documentclass[12pt,letterpaper]{hmcpset}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}

% info for header block in upper right hand corner
\name{ }
\class{Math 55 - Section ---}
\assignment{Homework 1}
\duedate{Thursday, September 8, 2016}

\renewcommand{\labelenumi}{{(\alph{enumi})}}

\begin{document}

\problemlist{1, 2, 3, 4, 5, 6, 7, 8, 9}

\begin{problem}[1]
    Starting from Washington DC, how many ways can you visit 5 of the 50 state capitals and return to Washington DC? (The order that you visit the capitals matters.)
\end{problem}
\begin{solution}
    \vfill
\end{solution}
\newpage

\begin{problem}[2]
    Find the number of 20-digit integers in which no two consecutive digits are the same. (We do not allow such a number to begin with zero.)
\end{problem}
\begin{solution}
    \vfill
\end{solution}
\newpage

\begin{problem}[3]
     How many ways can you seat 12 people at two distinct tables, where table 1 has 5 people and table 2 has 7 people? How does the answer change if both tables are circular (where arrangement ABCDE is the same as BCDEA)? (Give a numerical answer to each problem.)
\end{problem}
\begin{solution}
    \vfill
\end{solution}
\newpage

\begin{problem}[4]
    Let $B$ be a subset of $A$, where $|A|=n$, and $|B|=k$. What is the number of subsets of $A$ whose intersection with $B$ has exactly 1 element?
\end{problem}
\begin{solution}
    \vfill
\end{solution}
\newpage

\begin{problem}[5]
    How many different ``words'' can you get by arranging all the letters of the word MISSISSIPPI? (Give a numerical answer.)
\end{problem}
\begin{solution}
    \vfill
\end{solution}
\newpage

\begin{problem}[6]
    You want to send postcards to 12 friends. In the shop, there are only 3 kinds of postcards. In how many ways can you send the postcards if:
    \begin{enumerate}
        \item there is a large number of each kind of postcard, and you want to send one card to each friend;
        \item there is a large number of each kind of postcard, and you are willing to send one or more postcards to each friend (but no one should get two identical postcards);
        \item the shop has only 4 of each kind of postcard, and you want to send one card to each friend?
    \end{enumerate}
\end{problem}
\begin{solution}
    \vfill
\end{solution}
\newpage

\begin{problem}[7]
    The number of \textit{ternary} words of length $n$ is $3^n$ since each digit in the word has 3 choices (from the set $\{0,1,2\}$). How many ternary words of length $n$ exist where the digits 0, 1, and 2 each appear at least once? Also, give a numerical answer when $n=4$.
\end{problem}
\begin{solution}
    \vfill
\end{solution}
\newpage

\begin{problem}[8]
    Provide a combinatorial proof that for $n\geq2$ and $0\leq k\leq n$.
    \[
        \binom{n}{k}=\binom{n-2}{k}+2\binom{n-2}{k-1}+\binom{n-2}{k-2}.
    \]
\end{problem}
\begin{solution}
    \vfill
\end{solution}
\newpage

\begin{problem}[9]
    In the game of \textit{Octopoker} (just invented) a hand consists of 8 cards, where order is not important. Among the $\displaystyle\binom{52}{8}$ hands, count how many that have (numerical answer not required, but appreciated by grader):
    \begin{enumerate}
        \item at least one spade.
        \item 2 cards of each suit.
        \item every suit appears 1 or 2 or 3 times.
        \item exactly 3 different values. (Hint: break into 3 cases.)
    \end{enumerate}
\end{problem}
\begin{solution}
    \vfill
\end{solution}
\end{document}
